---
title: "Motor Trend Report"
author: "HPSUN"
date: "2017年12月3日"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Excutive Summary
For this analysis, We are using the mtcar dataset for analysis.For details of this dataset, your can see this link:   https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html  
We used linear regression model to evaluate the factor affact miles per gallon(mpg). And found that mpg prediction mainly depends on wt,cyl,disp of the car. The manual transmission may increase mpg a little (0.14), but it is not significant.So it's hard to say that auto transmission is better or not.

## Data Exploratory
```{r}
library(ggplot2)
data("mtcars")
#summary(mtcars)
m <- mtcars
m$cyl <- as.factor(m$cyl)
m$vs <- as.factor(m$vs)
m$am <- as.factor(m$am)
m$gear <- as.factor(m$gear)
m$carb <- as.factor(m$carb)
```

## Regression Model
From figure 1, It seems all the features are correlated to mpg. So, first, we add all features for regression model.
```{r}
fit1 <- lm(mpg~.,data=m)
anova(fit1)
```
From this model, we found cyl, disp, wt are signifcant variables have effect on mpg.So next, we use only disp, wt, cyl and am to predict mpg.
```{r}
fit2 <- lm(mpg~disp+wt+cyl+am,data=m)
summary(fit2)
```
This model explains 83.76% of the variance. From this we see the manual transmisson increase 0.141212 mpg,but it's not significant.The most important factors affect mpg is still cyl and wt.

## Appendix
### Figure 1: Exploratory plot
```{r,fig.width=10,fig.height=10}
par(mfrow = c(3,4))
plot(mpg~.,data=m)
```

### Figure 2 : fit1 Diagnostic
```{r}
par(mfrow = c(2, 2))
plot(fit1)
```

### Figure 3 : fit2 Diagnostic
```{r}
par(mfrow = c(2, 2))
plot(fit2)
```




